---
title: "Weight Lifting Assessment Report"
output: html_document
---

```{r setup, include=FALSE}
  library(caret)
  load('project.RData')
  set.seed(1337)
```


## Loading in data
Since we can not make predictions based on empty cells, these will be also treated as NA columns.

```{r eval=FALSE}
  rawTraining = read.table(file = 'pml-training.csv', sep = ',', header = T, na.strings=c("","NA"))
  rawTesting = read.table(file = 'pml-testing.csv', sep = ',', header = T)
```

## Cleaning the data

I am removing the first 7 columns, because these values are not important for our prediction. They contain user info and time data. Also I am removing all columns that had NA values inside. Then I am preprocessing so that the data is centered and scaled.
```{r eval=FALSE}
  trainingClean = rawTraining[,c(-1:-7)]
  trainingNa <- trainingClean[,colSums(is.na(trainingClean)) == 0]
  trainingPre = predict(preProcess(trainingNa), trainingNa)
```

## Splitting the data
Finally I am splitting the data into training and validation dataset.
```{r eval=FALSE}
  inTrain = createDataPartition(trainingPre$classe, p = 3/4)[[1]]
  training = trainingPre[ inTrain,]
  validation = trainingPre[-inTrain,]
```

## Building the model

First of all, I am setting the train control parameters. I am using k-fold cross-validation, original training data is partitioned into 10 subsamples.
```{r eval=FALSE}
trainctrl <- trainControl(verboseIter = TRUE, method="cv",number=10)
```
For training algorithm I chose rf, which is random forests.
```{r eval=FALSE}
modelRf = train(data = training, classe ~ ., method = 'rf', trControl = trainctrl)
```
After model is ready, I am testing it on my validation set and checking the accuracy
```{r eval=F}
predRf = predict(modelRf, newdata = validation)
predRfConf = confusionMatrix(validation$classe, predRf)
```
Validation shows that accuracy is 0.9957, which is almost perfect.
```{r }
predRfConf
``` 